Application-Level Regression Testing Framework using Jenkins

### 2017-03-02 manuscript/manuscript.tex
cleaned up security section

Our Jenkins instance was deployed on a vSphere managed VM running Centos 6.8. Security was of the highest concern since Jenkins has the ability to execute commands on our login nodes. Jenkins is set to log in as a standard user account with passwordless access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM. The VM (bwjenkins) was closely vetted by our security team on our test and development system (TDS) before it was allowed access to Blue Waters. Iptables was used to lock bwjenkins down to a small internal ip space to ensure the highest security. An anonymous user account was enabled with ‘read-only’ access to view current and historical test results. During a test, Jenkins downloads software, builds the software, submits a job, awaits completion, gathers and plots the results or returns error information during a failure. These are full end to end functionality testing of the programming environment, queueing system, license servers and provide historical metrics to quickly detect regressions.

@@

\subsection{Security Considerations}
Blue Waters is an OTP only restricted access system. Enabling Jenkins access to Blue Waters posed some unique security hurdles that we had to overcome. Jenkins has the ability to execute commands on our login nodes. Jenkins is set to log in as a standard user account with passwordless access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM. We restricting access to the physical VM and Jenkins GUI (bwjenkins) utilizing iptables, SSL and OTP. The VM allows restricted host-based ssh (port 22) access from two secure OTP only administrative systems. The Jenkins GUI presented additional challenges. We setup reverse proxy to run Jenkins behind apache/http with SSL for access to the administrative console. All the configuration is in /etc/httpd/config.d/ssl.conf. An anonymous GUI view was setup (config file snippets below)

@@

\subsection{Configuration Choices}

>>>>

Our Jenkins instance was deployed on a vSphere managed VM running Centos 6.8. Security was of the highest concern since Jenkins has the ability to execute commands on our login nodes. Jenkins is set to log in as a standard user account with pass-wordless access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM. The VM (bwjenkins) was closely vetted by our security team on our test and development system (TDS) before it was allowed access to Blue Waters. Iptables was used to lock bwjenkins down to a small internal ip space to ensure the highest security. An anonymous user account was enabled with ‘read-only’ access to view current and historical test results. During a test, Jenkins downloads software, builds the software, submits a job, awaits completion, gathers and plots the results or returns error information during a failure. These are full end to end functionality testing of the programming environment, queueing system, license servers and provide historical metrics to quickly detect regressions.

@@

\subsection{Security Considerations}
Enabling Jenkins access to Blue Waters posed some unique security hurdles that we had to overcome. Blue Waters is an OTP only restricted access system. Jenkins has the ability to execute user-level commands on our login nodes. Jenkins has some unfortunate default settings. The access control is set to "Jenkins' own user database," and the "Allow users to sign up" option is enabled, so if you don't have an account, you can create one by providing your name, e-mail and a password. Additionally, there's an authorization option enabled which says "Logged-in users can do anything." So, once you complete the sign up form, you have full admin access to the system.  This required us initially to test the deployment with our test and development (TDS) CRAY. This resulted in the following requirements. Restricted OTP access to the physical system that will host Jenkins. In addition, OTP only access to the Jenkins GUI command console that must be contained within our IP space.  The Jenkins GUI will also restrict the command console access to our Blue Waters LDAP server.

\subsection{Configuration Choices}
Jenkins instance was deployed on a vSphere managed VM running Centos 6.8. The VM allows restricted host-based ssh access from two secure OTP only administrative systems. The Jenkins GUI presented additional challenges. The Jenkins GUI is configured to log in as a standard user account with pass-wordless access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM. We restricting access to the physical VM and Jenkins GUI (bwjenkins) utilizing iptables, SSL and OTP.  A reverse proxy was used to run Jenkins behind apache/http with SSL for access to the administrative console. All the configuration is in /etc/httpd/config.d/ssl.conf. Anonymous access to the Jenkins GUI was allowed for limited read only view of test status and historical plots. The Anonymous access view is not restricted. \\
(config file snippets below)

@@
